The Occurrence of Earth-Like Planets Around Other Stars

### 2014-04-17 paper/kepler-selection.tex
Abstract changes, per Ilya's suggestions.

\begin{abstract}
  The quantity $\etaearth$, the number density of planets per star per
  logarithmic planetary radius per logarithmic orbital period,
  describes the occurrence of Earth-like extrasolar planets.
  Measurement of $\etaearth$ is complicated by the difficulty of
  detecting Earth-like planets in Earth-like orbits about Sun-like
  stars; previous estimates place $1\% \lesssim \etaearth \lesssim
  34\%$, relying on extrapolations from regions in period-radius space
  where detection is easier and the sample of observed planets is
  complete\cite{2011ApJ...738...81W,2011ApJ...738..151C,2012ApJ...745...20T},
  or modelling the selection effects carefully but using simpler
  models of the period-radius distribution of
  exoplanets\cite{2013ApJ...778...53D}, possibly using a low-noise
  subset of the available data\cite{2013PNAS..11019273P}.
  Additionally, no previous estimates account for contamination from
  false-positive planetary identifications.  Here we present
  constraints on $\etaearth$ from a parameterised forward model of the
  (correlated) period-radius distribution and the observational
  selection function in the most recent (Q17) data release from the
  Kepler
  satellite\cite{2010Sci...327..977B,2011ApJ...736...19B,2013ApJS..204...24B},
  including an empirical parameterisation for the distribution of
  false-positives in the data set.  We find $\etaearth =
  4.1^{+2.3}_{-1.7}\%$ (90\% CL).  Additionally, we find that each
  star hosts $4.04_{-0.68}^{+0.85}$ planets with $P \lesssim 3
  \mathrm{yr}$ and $R \gtrsim 0.2 \REarth$, that the peak of the
  planet-radius distribution lies at $\Rpeak = 1.19_{-0.18}^{+0.17}
  \REarth$.  \Will{More science stuff here.}
\end{abstract}

>>>>

\begin{abstract}
  The quantity $\etaearth$, the number density of planets per star per
  logarithmic planetary radius per logarithmic orbital period,
  describes the occurrence of Earth-like extrasolar planets.
  Measurement of $\etaearth$ is complicated by the difficulty of
  detecting Earth-like planets in Earth-like orbits about Sun-like
  stars; previous
  estimates\cite{2011ApJ...738...81W,2011ApJ...738..151C,2012ApJ...745...20T,2013ApJ...778...53D,2013PNAS..11019273P}
  place $1\% \lesssim \etaearth \lesssim 34\%$.  Here we present
  constraints on $\etaearth$ from a parameterised forward model of the
  (correlated) period-radius distribution and the observational
  selection function in the most recent (Q17) data release from the
  Kepler
  satellite\cite{2010Sci...327..977B,2011ApJ...736...19B,2013ApJS..204...24B}.
  We parameterise the intrinsic distribution of planetary periods and
  radii using a single, correlated Gaussian component; treat selection
  effects using a parameterised transit detection probability based on
  the measured noise level and stellar properties in the Kepler
  catalog; and include an empirically-parameterised, independent
  component in the planet period-radius distribution to represent
  false-positive planet detections.  We find $\etaearth =
  4.1^{+2.3}_{-1.7}\%$ (90\% CL).  Additionally, we find that each
  star hosts $4.04_{-0.68}^{+0.85}$ planets with $P \lesssim 3
  \mathrm{yr}$ and $R \gtrsim 0.2 \REarth$ and that the peak of the
  planet radius distribution lies at $\Rpeak = 1.19_{-0.18}^{+0.17}
  \REarth$ (all 90\% CL).  Our empirical model for false-positive
  contamination is consistent with the dominant source being backgroud
  eclipsing binary stars, with $1.1_{-0.18}^{+0.2} \times 10^{-3}$
  false-positives per star.  \Will{More science stuff here.}
\end{abstract}
